A Comparison of Use-Case Based and Checklist- Based Reading: A Controlled Experiment

### 2015-03-17 rmtw/a3/latex8.tex
hi john

\documentclass[10pt,twocolumn]{article} 
\usepackage{latex8}
\usepackage{url}

@@

\title{Implementing Change in Multi-paradigm Environments, a Case Study}

@@

\SubSection{Existing Literature}
According to literature, changes in companies are commonly implemented following either Software Process Improvement (SPI)\cite{pettersson2008practitioner}\cite{unterkalmsteiner2012evaluation} or change management (CM) strategies. SPI is an attempt to alter an existing company or organisations software process, the main intention of which is to increase product quality, time to market all the while reducing inefficiency and other obstacles for creating good software.

@@

\SubSection{Case Study Design}
The study has been conducted with an exploratory goal in mind. Analysing how Ericsson tackle the problems related to the research questions has been the central part of the study. Due to the exploratory nature of the study, a flexible process design has been used. The study has been carried out using an iterative approach, where the data collected, and the results gathered from analysing the data has been the main driver for shaping and improving the scope and goal of the study.

The methodology used has been case study. The reason for this is that the goal of our study is to analyse how changes are implemented in the context of multi-paradigm development environments in software engineering. This line of thought is supported by Runesson \& Höst in \cite{runeson2009guidelines}. Runesson \& Höst also outline that a case study approach is well-suited for exploratory studies \cite{runeson2009guidelines}. Another reason for conducting this study using a case study approach is that there is little existing research conducted in the area, and that input from industry is vital to the success of the research.

During the initial stage of the study, careful planning was conducted. The two major goals of this phase were to find meaningful objectives with an appropriate design for the research and secondly to facilitate and design the interviews. Although a flexible approach was taken, major effort was spent on planning the study. Most of the planning was related to communicating with Ericsson to facilitate the interviews. A time-line for the interviews was created and established with Ericsson. The objective of analysing change implementation in environments which are split into by two different development activities was also defined during this stage. The case study protocol \cite{brereton2008using} developed and used during this phase can be seen in Table 1. The protocol can be viewed as a high-level timeline for our study.

\begin{table}
	\centering
	\begin{tabular}[Ht]{|l|p{3cm}|p{3.5cm}|}
	\hline
	\textbf{Phase} & \textbf{Activity} & \textbf{Description} \\
	\hline
	1 & Background & Identify related work and research questions \\
	\hline
	2 & Case Study Design & Design the case study, identify object of the study \\
	\hline
	3 & Case Selection & Define criteria for case selection \\
	\hline
	4 & Roles and Responsibilites & Plan and decide roles and responsibilites for researchers \\
	\hline
	5 & Data Collection & Design the data collection phase \\
	\hline
	6 & Data Analyis & Design the data analysis phase \\
	\hline
	7 & Validity & Design plan for how to reduce validity threats \\
	\hline
	8 & Remaining Validity & Identify remaining threats to validity \\
	\hline
	9 & Design Reporting & Identify target audience \\
	\hline
	10 & Schedule & Design a schedule and estimate time for each phase \\
	\hline

	\hline
	\end{tabular}
	\caption{Case Study Protocol}
\end{table}

@@

\newpage
\appendix

@@

>>>>

\documentclass[10pt,twocolumn]{article} 
\usepackage{latex8}
\usepackage{url}
\usepackage[toc,page]{appendix}

@@

\title{Implementing Change in Multi-paradigm Environments: a Case Study}

@@

\SubSection{Related Work}
According to literature, changes in companies are commonly implemented following either Software Process Improvement (SPI)\cite{pettersson2008practitioner}\cite{unterkalmsteiner2012evaluation} or change management (CM) strategies. SPI is an attempt to alter an existing company or organisations software process, the main intention of which is to increase product quality, time to market all the while reducing inefficiency and other obstacles for creating good software.

@@

\SubSection{Case Study Design}
The study has been conducted with an exploratory goal in mind. Analysing how Ericsson tackle the problems related to the research questions has been the central part of the study. Due to the exploratory nature of the study, a flexible process design has been used. The study has been carried out using an iterative approach, where the data collected, and the results gathered from analysing the data have been the main driver for shaping and improving the scope and goal of the study.

The methodology used has been case study. The reason for this is that the goal of our study is to analyse how changes are implemented in the context of multi-paradigm development environments in software engineering. This line of thought is supported by Runesson \& H\"{o}st in \cite{runeson2009guidelines}. Runesson \& H\"{o}st also outline that a case study approach is well-suited for exploratory studies \cite{runeson2009guidelines}. Another reason for conducting this study using a case study approach is that there is little existing research conducted in the area, and that input from industry is vital to the success of the research.

During the initial stage of the study, careful planning was conducted. The two major goals of this phase were to find meaningful objectives with an appropriate design for the research and secondly to facilitate and design the interviews. Although a flexible approach was taken, major effort was spent on planning the study. Most of the planning was related to communicating with Ericsson to facilitate the interviews. The objective of analysing change implementation in environments which are split into by two different development activities was also defined during this stage.

A case study protocol \cite{brereton2008using} was developed and used as a formal plan for the study. The main reasons for using a case study protocol were to have a solid plan that is reviewable by other researchers, and to make sure that all researchers had a common strategy for conducting the study. The case study protocol served as a plan for the whole duration of the research. A list of which areas were planned and described in the case study protocl can be seen in Table 1.

\begin{table}
	\centering
	\begin{tabular}[Ht]{|c|l|}
	\hline
	\textbf{Phase} & \textbf{Activity}\\
	\hline
	1 & Background 1\\
	\hline
	2 & Case Study Design \\
	\hline
	3 & Case Selection \\
	\hline
	4 & Roles and Responsibilites \\
	\hline
	5 & Data Collection \\
	\hline
	6 & Data Analyis \\
	\hline
	7 & Validity Design \\
	\hline
	8 & Remaining Validity \\
	\hline
	9 & Reporting Design \\
	\hline
	10 & Schedule \\
	\hline

	\end{tabular}
	\caption{Case Study Protocol}
\end{table}

@@

\newpage
\begin{appendices}

@@

\end{appendices}

### 2015-03-17 rmtw/a6/latex8.tex
hi john

\section{Introduction}
%Literature intro
%A bit unclear what to write here - check with Branson

\subsection{Problem Statement}

\subsection{Purpose Statement}

\subsection{Research Questions}

@@

\section{Case Company Description}
*Not sure if this should be a sub-heading somewhere

>>>>

\section{Introduction}
%Literature intro
%A bit unclear what to write here - check with Branson
Explain what APIs are. 
Explain how and that APIs change. (Link it to the software evolution in a nice way).

\subsection{Problem Statement}
1.

\subsection{Purpose of the Study}
Academia: 
The results of what *actually* (i.e. our study) affects APIs could be compared to what literature says should affect design (i.e. best practices).

Industry: 
If a company can study their API's evolution and be able to track changes and design decisions, it can give them more knowledge to further improve and develop their API.

If companies can identify changes, they can also identify what *was* bad.

Changing APIs is usually not a good thing. If you can identify what changes APIs you can spend more time on that in development to avoid too much change in the future.

\subsection{Research Questions}
RQ1: What drives API evolution? 
SRQ1: To what extent can we reverse engineer API change decisions?
SRQ2:

@@

\section{Case Company Description}
